The Spatial and Temporal Domains of Modern Ecology

### 2017-12-18 paper/main.tex
Revising main text to include information on observational type distributions, and updated figure 1 vignette to produce percentage of observations per bin by observations type

\noindent \textbf{\emph{Domains}}\\
In terms of resolution, the majority (67\%) of observations were collected in plots of $<$1 m$^2$ resolution, 24\% were collected within plots of 1 m$^2$ up to 1 ha, and the remaining 9\% in plots of $\geq$1 ha (Fig. 1A). The extent of 19\% of observations was $<$10 ha, 23\% covered 10-1,000 ha, 12\% 1,000-10,000 ha, 19\% 10,000-100,000 ha, 12\% 100,000-1,000,000 ha, and 15\% $>$1,000,000 ha (Fig. 1B).

>>>>

\noindent \textbf{\emph{Domains}}\\
In terms of resolution, the majority (67\%) of observations (across all methods) were collected in plots of $<$1 m$^2$ resolution, 24\% were collected within plots of 1 m$^2$ up to 1 ha, and the remaining 9\% in plots of $\geq$1 ha (Fig. 1A). These distributions primarily reflect those of field observations, the dominant observational methodology. Examining the distributions for each observational method (Fig. S1 in SI) shows that automated sensing and paleo-reconstruction had resolutions that were generally finer ($<$0.1 m$^2$) than field observations, while remote observations were generally coarser ($>$100 m$^2$).

The extent of 19\% of observations was $<$10 ha, 23\% covered 10-1,000 ha, 12\% 1,000-10,000 ha, 19\% 10,000-100,000 ha, 12\% 100,000-1,000,000 ha, and 15\% $>$1,000,000 ha (Fig. 1B).  As with resolution, the extent of automated observations tended to be finer
